---
title: "Proyect Statistics"
author: 
- "Luis Fernando Monterrubio Cota"
- "Karina Campos Almeida"
- "Cynthia Vidal Ovando"
- "Brianna Ayelen Balam Velasco"
- "Edoardo Alonso Martinez Perez"
date: '2022-05-16'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(kableExtra)
library(tidyverse)

mode <- function(x) {
   return(as.numeric(names(which.max(table(x)))))
}
```

##INTRODUCTION

We used an INEGI database on the general population of the country, then we extracted a sample of people studying and not studying in an age range from 3 years old to 14 years old in the whole country.

```{r censo, echo=FALSE}
censo <- read.csv("diccionario_de_datos/INE_ENTIDAD_2020.csv",sep =",", dec = ",", header = T, encoding = "UTF-8")
str(censo)
```

##DATA

To proceed we need to have 3 data of education in each state of the Republic:

1.  Students
2.  Who do not study
3.  Population in the age range.

After having our database and extracting the information of the people who do not study and the population in the range of 3 to 14 years, we obtain the people who do study and we get the total of the three types of people.

```{r cleaning, echo=FALSE}
total <- censo %>% 
  select(ENT, NOM_ENT, P3A5_NOA, P6A11_NOA, P12A14NOA, P_3A5, P_6A11, P_12A14)%>%
  rename(STATE = NOM_ENT, Age_3_5 = P3A5_NOA, Age_6_11 = P6A11_NOA, Age_12_14 = P12A14NOA, Age_3_5_ = P_3A5, Age_6_11_ = P_6A11, Age_12_14_ = P_12A14)%>%
  mutate(Total_no_study = Age_3_5 + Age_6_11 + Age_12_14) %>%
  mutate(Total_population = Age_3_5_ + Age_6_11_ + Age_12_14_) %>%
  select(ENT, STATE, Total_no_study, Total_population) %>%
  mutate(Total_study = Total_population - Total_no_study)

Total <- total %>%
  select_if(is.numeric) %>%
  colSums()

Total <- bind_rows(total, Total)
Total[(dim(Total)[1]), 1] = "$"
Total[(dim(Total)[1]), 2] = "Total"

rm(censo)

Total %>%
  kbl() %>%
  kable_styling()
```

##TABLE WITH FREQUENCY 

```{r Table, echo=FALSE}
frecuencia <- read.csv("diccionario_de_datos/frecuencia.csv", sep = ",", dec = ";", header = T)

frecuencia %>%
  kbl() %>%
  kable_styling()
```

##RESULTS

Once we have our data organized, we are going to process what we have obtained and take some measurements such as:

1. Average
2. Median
3. Mode
4. Variance
5. Standard Deviation

```{r results, echo=FALSE}
results <- data.frame(
  "Measures" = c("Mean", "Median", "Mode", "Variance", "Standard Deviation"),
  "Total_study" = round(c(mean(total$Total_study), median(total$Total_study), mode(total$Total_study), var(total$Total_study), sd(total$Total_study))),
  "Total_no_study" = round(c(mean(total$Total_no_study), median(total$Total_no_study), mode(total$Total_no_study), var(total$Total_no_study), sd(total$Total_no_study))),
  "Total_population"= round(c(mean(total$Total_population), median(total$Total_population), mode(total$Total_population), var(total$Total_population), sd(total$Total_population))))

results %>%
  kbl() %>%
  kable_styling()

```
##PLOTS

```{r, echo=FALSE}
ggplot(data = total, aes(x = STATE, y = Total_study, fill = "red")) + geom_bar(stat = "identity") + labs(title = "STUDENTS IN MEXICO", x = "States", y = "Students") + theme(axis.text = element_text(angle = 90))

ggplot(data = total, aes(x = STATE, y = Total_no_study)) + geom_bar(stat = "identity") + labs(title = "NO STUDENTS IN MEXICO", x = "States", y = "No students") + theme(axis.text = element_text(angle = 90))
```

##CONCLUSIONS


##REFERENCES

https://www.inegi.org.mx/app/descarga/default.html
